Efficiently summarizing relationships in large samples: a general duality between statistics of genealogies and genomes

### 2020-01-18 treestats_paper.tex

All methods described here are implemented in python and C in the package \tskit{},
available from \url{https://github.com/tskit-dev/tskit}
under the terms of the MIT license.
All code used to produce the figures in this paper
is available from \url{https://github.com/petrelharp/treestats_ms}.

>>>>

All methods described here are implemented in Python and C in the package \tskit{},
available from \url{https://github.com/tskit-dev/tskit}
under the terms of the MIT license.
All code used to produce the figures in this paper
is available from \url{https://github.com/petrelharp/treestats_ms}.
